A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & -1292.89 & 0.79 & -1292.89 & 0.20 & 0.11 \\
Cox & -- & 0.80 & -- & 0.12 & 0.06 \\
Log Logistic & -1474.32 & 0.79 & -1474.32 & 0.17 & 0.10 \\
Log Normal & -1459.29 & 0.79 & -1459.29 & 0.18 & 0.11 \\
\bottomrule
\end{tabular}
\end{table*}
